### 2020-11-10 README.Rmd
switched GH action to a more standard one for packages.

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/BrunaLab/HeliconiaDemography/master?urlpath=rstudio) 
[![R build status](https://github.com/BrunaLab/HeliconiaDemography/workflows/run-tests/badge.svg)](https://github.com/BrunaLab/HeliconiaDemography/actions)

<!-- badges: end -->

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/BrunaLab/HeliconiaDemography/master?urlpath=rstudio) [![R build status](https://github.com/BrunaLab/HeliconiaDemography/workflows/R-CMD-check/badge.svg)](https://github.com/BrunaLab/HeliconiaDemography/actions)
<!-- badges: end -->
